Turbulence in compact to giant H~II regions

### 2023-04-21 strucfunc_paper.tex
Finish revisions of Carina in Appendix C

% We follow the same procedure we use to describe the observed structure function of the Orion Nebula for the rest of the regions.
Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
The model fit gives \(\sigma\pos^2 = \SI{7 \pm 1}{km^{2}.s^{-2}}\), \(r_0 = \SI{1 \pm 0.2}{pc} \), and \(m = 1.26 \pm 0.2\).
In this case, there is good agreement between the model value and empirically value of \(\sigma\pos^2\),
indicating that finite box effects are unimportant.
On the other hand, the model-derived \(m\) is steeper than would be naively derived
from the observations, which is a symptom of the effects  of noise.
At separations smaller than the correlation length, the structure function shows irregular oscillations about the mean ascending trend,
which are a symptom of the relatively small number of spatial points in this source.

@@

The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc} ; \citealp{2006ApJ...644.1151S}}.
It contains young clusters like Trumpler 14 and 16, and Collinder 228 from the Car OB1 association, one of the largest OB associations in the Galaxy.
This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars and the most luminous star is the blue variable $\eta$ Car.
The ionizing flux \(Q_0\) is \SI{e50.95}{photons.s^{-1}} \citep{2008hsf2.book..138S} (60 times higher compared to the Orion Nebula) and the luminosity in \ha{} of \SI{e39.01}{erg.s^{-1}}.
As a star formation region, it presents several phenomena related with young stars as evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars and Herbig-Haro objects, to mention some \citetext{see \citealp{2008hsf2.book..138S} and reference therein}. 
This region can be consider as a bridge between the detailed star-formation regions like Orion, and much more distant regions like 30 Doradus.

@@

The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
As the Lagoon nebula, the structure function of Carina also shows a non-uniform and a more disperse behavior below the correlation length.
The value of the observed \(\sigma\pos^2 = \SI{18}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{0.5}{pc} \) (in this case there is a good agreement with the derived values from our model which are \(\sigma\pos^2 = \SI{18}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.5}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{1.6}{pc} \).
Above this separation, at larges scales, the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
Also, it can be argue that at large scales the behavior does not reflect purely the homogeneous fluctuations. 
It seems that there are two  oscillating pattern at large scales.
The first one, from \(r = \SI{1.7}{pc} \) to \SI{6}{pc} which has an spatial wavelength of \SI{\sim 2}{pc} and a dispersion of \SI{1}{km^{2}.s^{-2}}.
The second one when \(r >\)\SI{6}{pc} until \SI{7}{pc} with a dispersion of \SI{3.5}{km^{2}.s^{-2}}.
This fluctuations are around the value of 2\(\sigma^2\pos\) so it is possible that the dispersion is artificial because of the multi-fiber observations (see section~\ref{sec:flames-multi-fiber}).
There aren't any points affected by the seeing (RMS) which has a value of \SI{0.015}{pc} (\(s_0\)=\SI{3.4}{\arcsecond}).
If we consider the first point of this \(B(r)\) to be valid, which corresponds to \SI{4}{km^{2}.s^{-2}} at \(r = \SI{0.01}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.38} and \num{0.43}, respectively, while our derived value is \num{1.16}.

>>>>

% We follow the same procedure we use to describe the observed structure function of the Orion Nebula for the rest of the regions.
Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
The model fit gives \(\sigma\pos^2 = \SI{7 \pm 1}{km^{2}.s^{-2}}\), \(r_0 = \SI{1 \pm 0.2}{pc} \), and \(m = 1.26 \pm 0.2\).
In this case, there is good agreement between the model value and empirical value of \(\sigma\pos^2\),
indicating that finite box effects are unimportant.
On the other hand, the model-derived \(m\) is steeper than would be naively derived
from the observations, which is a symptom of the effects  of noise.
At separations smaller than the correlation length, the structure function shows irregular oscillations about the mean ascending trend,
which are a symptom of the relatively small number of spatial points in this source.

@@

The Carina nebula is a large star-forming complex located at a distance of \SI{2 350}{pc} \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc}; \citealp{2006ApJ...644.1151S}}.
It contains young clusters like Trumpler~14 and~16, and Collinder~228 from the Car~OB1 association, one of the largest OB associations in the Galaxy.
This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars and the most luminous star is the blue variable $\eta$~Car.
The ionizing flux \(Q_0\) is \SI{e50.95}{photons.s^{-1}} \citep{2008hsf2.book..138S} (60 times higher compared to the Orion Nebula) and the luminosity in \ha{} of \SI{e39.01}{erg.s^{-1}}.
As a high-mass star formation region, it presents several phenomena related to young stars,
such as evaporating protoplanetary discs, erosion of large dust pillars, and the triggering of a second generation of embedded stars and Herbig-Haro objects \citetext{see \citealp{2008hsf2.book..138S} and reference therein}. 
This region is at an intermediate scale between nearby regions like Orion
that are dominated by a single star, and giant star formation regions such as 30~Doradus.

@@

Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
The model fit gives \(\sigma\pos^2 = \SI{18 \pm 2}{km^{2}.s^{-2}}\), \(r_0 = \SI{0.6 \pm 0.1}{pc} \), and \(m = 1.2 \pm 0.3\).
Again there is good agreement between the model value and empirically measured
value of \(\sigma\pos^2\),
indicating that finite box effects are unimportant. In addition, both noise and seeing are
found to be unimportant. 
Similarly to the Lagoon nebula,
the structure function of Carina also shows a non-uniform and irregular behavior
below the correlation length, which can again be ascribed to the sparse spatial sampling.
As a result of this, the power-law slope determination is not very precise.

On scales larger than the correlation length,
the structure function of the Carina nebula is remarkably flat
for \(r = 2\) to \SI{6}{pc},
in good agreement with the prediction of homogeneous fluctuations
(Figure~\ref{fig:model-strucfunc}a).
But at the largest scales accesible to our observations, there is evidence for low-amplitude
periodic fluctuations with a wavelength of \(\lambda \approx \SI{8}{pc}\),
which corresponds to the typical separation
between the individual star clusters that make up the complex
(for instance, between Tr~14 and Tr~16).
